---
title       : Week 4 Shiny Project
subtitle    : A small DNA/RNA sequence analysis tool
author      : Xiaolong He
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, shiny, interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Introduction

This shiny application accepts DNA or RNA sequence as the input and performs following analysis

1. Find the length of the sequence
2. Calculate the proportion of each base in the sequence
3. Find the complementary sequence
4. Find the amino acid sequence encoded by the sequence

--- 

## Input

Following are the examples of input sequences
<p style="text-align: justify; word-break: break-all; font-size: 50%;">
DNA: <br/>
TCTAACAAGAAGGACATTGATGACAACAGCAATGGAACCTATGAGAAAATGCAAAACTCAGCACCACGAAAACAAAGAGGACAGAGAAAAGAACGATCTCCTCAGCAGAATATAGTATCTTGTGTAAGTGTAAGCACCCAGACAGCTTCAGATGATCAAGCTGGTAAACTGTGGGATGAACTCAGTCTGGTTGGGCTTCCAGATGCCATTGATATCCAAGCCTTATTTGATTCTACAGGCACTTGTTGGGCTCATCACCGTTGTGTGGAGTGGTCACTAGGAGTATGCCAGATGGAAGAACCATTGTTAGTGAACGTGGACAAAGCTGTTGTCTCAGGGAGCACAGAACGATGTGCATTT
 <br/> <br/>
RNA: <br/>
AGGCAGAACGGUCGCCGCGUCGCCUCAGCACGGACCUCCAGGGAGCUCCUCAGCAAGAUCCUGCCAGGGCGCCCCUCAGCGCGAUUCUGCCGGGGUGCCUCUCAGCGUGGUCCUCCCCGGGGCUCCUCAGCACGAUUCUCCCGGUGCGCCCCUCAGCGCGGUCCUCCUCGGUGCGUCAGUCAUCGUGGUUCUCCCCGGCGCGCCCCUCGGCGCGGUUCUCCUCGGGGCUCCUCAGCGCGGCGCUCUUCUGGGGGCUCCUCGGCGCAGUUCUCCCCGGGGACUCCUCGGCGCCGUUCUCCUCGGGGCACCCGGGGCUUUUCGGCGCGGUUCUCCCCGGGGGUUCUUCGGCGCGGUUGUCCC
</p>

---

## User Interface

```{r opts.label='shiny'}
library(shiny)

slidifyUI(
      titlePanel(h3("Sequence Analysis Tool")),
  # Sidebar panel for input of DNA sequence and selection of analysis 
    sidebarPanel(
       textAreaInput("na1",
                   "Please input your DNA Sequence below:", width='100%', rows = 10, placeholder = "DNA Sequence...", resize="vertical"),

    checkboxGroupInput("todo1", "Check what you want to run:", c("Length", "Nucleotide composition", "Complementary sequence", "Amino acid sequence"), width="100%"), 
    class='span4'
    ),
    
    # Show the results of analysis
    mainPanel()
)
```

---

## Functional Shiny Application
You can test the application with the sequence in the text box or your own DNA or RNA sequence
```{r opts.label='shiny'}
library(shiny)

slidifyUI(
      titlePanel(h3("Sequence Analysis Tool")),
  # Sidebar panel for input of DNA sequence and selection of analysis 
    sidebarPanel(
       textAreaInput("na2",
                   "Please input your DNA Sequence below:", width='100%', rows = 10, value="AATAAACTAGTTGAGAAGCAGAACCCAGCTGAAGGACTGCAAACTTTGGGGGCTCAAATGCAAGGTGGTTTTGGAT", resize="vertical"),

    checkboxGroupInput("todo", "Check what you want to run:", c("Length", "Nucleotide composition", "Complementary sequence", "Amino acid sequence"), width="100%"), 
    class='span4'
    ),
    
    # Show the results of analysis
    mainPanel(
       conditionalPanel(
            condition = "input.todo.indexOf('Length') != -1",
            h4(strong("Length of the sequence")),
            h4(textOutput("len"))
       ),
       conditionalPanel(
           condition = "input.todo.indexOf('Nucleotide composition') != -1",
           h4(strong("Proportion of each base in the sequence")),
           plotOutput("comp")
       ),
       conditionalPanel(
           condition = "input.todo.indexOf('Complementary sequence') != -1",
            h4(strong("Complementary sequence of the DNA")),
            p(textOutput("compl"))
        ),
       conditionalPanel(
           condition = "input.todo.indexOf('Amino acid sequence') != -1",
           h4(strong("Open reading frames encoded by the sequence")),
           p(textOutput("tr"))
       )
    )
)

```